---
title: "Shiny Project Presentation"
author: "Emily Stone"
date: "25/08/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This App allows you to explore the mtcars data set. 

The member can select the variable that they with to model, the dependent variables they wish to be included in multi-variate regression and the dependent variable they wish for the independent variable to be plotted against.

The App then produces a summary of the model coefficients in table.

## The data 

The table below shows the data used by the APP

```{r, echo = TRUE}
head(mtcars)
```

## The User interface

The UI code was as follows

```{r, echo = TRUE,eval= FALSE}
library(shiny)

dat <- mtcars

shinyUI(pageWithSidebar(
    headerPanel("Multivariate regression on the motor cars data set"),
    
    sidebarPanel(
        selectInput("dependent", "Dependent Variable:", names(dat)),
        uiOutput("independent")
    ),
    
    mainPanel(tableOutput("regTab"))
))
```

## The server
The server code was as follows

```{r, echo = TRUE,eval= FALSE}
library(shiny)

dat <- mtcars
library(ggplot2)

shinyServer(function(input, output, session) {
    
    output$independent <- renderUI({
        checkboxGroupInput("independent", "Independent Variables:",names(dat)[!names(dat) %in% input$dependent],names(dat)[!names(dat) %in% input$dependent])
    })
    
    runRegression <- reactive({
        lm(as.formula(paste(input$dependent," ~ ",paste(input$independent,collapse="+"))),data=dat)
    })
    

```


## The server continued

```{r, echo = TRUE,eval= FALSE}

    output$regTab <- renderTable({
        if(!is.null(input$independent)){
            summary(runRegression())$coefficients
        } else {
            print(data.frame(Warning="Please select Model Parameters."))
        }
    }, include.rownames=TRUE)
})
    
 

```

## An example of the output

Suppose a member selected the following:

-  Dependent variable: hp
-  Independent variables: mpg, cyl


It would produce the following table:
```{r, echo = FALSE,eval= TRUE}
regression<- lm(hp~ mpg +cyl,data=mtcars)
summary(regression)$coefficients
```







